Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-09 project.Rmd
plot periodgram on original scale

## Periodgram
```{r periodgram}
min_h_seasonality <- 24
min_h_seasonality <- 2
pgram <- spec.pgram(stats::filter(build_ts(seis.h, start = seis.train.start, end = seis.train.end), side=2, filter=c(0.5, rep(1,min_h_seasonality-1), 0.5)/min_h_seasonality),
#`pgram <- spec.pgram(build_ts(seis.h, start = seis.train.start, end = seis.train.end),
                    detrend=F, demean=T, na.action=na.aggregate, plot=F)
pgram.data <- data.frame(freq=pgram$freq, spec=pgram$spec)
ggplot(pgram.data) +
  geom_line(aes(freq, log(spec))) +
  xlab("frequency") + ylab("log(spectrum)") +
  labs(title = "Periodgram", caption = paste0("bandwidth = ", pgram$bandwidth, "    df = ", pgram$df)) ->
  periodgram

@@

ratio.color <- function(x) ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*3), "red", ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*2), "blue", ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*1), "darkgreen", "orange")))
shown_labels <- 4
periodgram +
  scale_x_continuous(sec.axis = sec_axis(~1/./3600, breaks=c(1, 3, 2*c(1,2,3,4,6,12), 24*7), labels = as.integer, name="hours")) +
  scale_y_continuous(sec.axis = sec_axis(~exp(.), breaks=mean(pgram$spec) + sd(pgram$spec) * c(1,3), labels=c("1", "2", "3")[c(1,3)], name="spectrum/sd ratio")) +
  geom_hline(yintercept=log(mean(pgram$spec) + sd(pgram$spec) * c(1:3)), linetype="dotted", color = ratio.color(mean(pgram$spec) + sd(pgram$spec) * c(1:3))) +
  geom_point(data=data.frame(freq=top95freq, spec=top95pc), aes(freq, log(spec), color=ratio.color(spec)), shape="o", size=4, show.legend = F) +
  geom_label_repel(data=data.frame(freq=top95freq, spec=top95pc)[1:shown_labels,], aes(freq, log(spec), label=round(1/freq/3600), color=ratio.color(spec)), segment.color="grey", show.legend=F) +
  scale_color_manual(values = c("darkgreen", "blue", "red")[start_ratio:3])

>>>>

## Periodgram
```{r periodgram}
min_h_seasonality <- 24
min_h_seasonality <- 2
pgram <- spec.pgram(stats::filter(build_ts(seis.h, start = seis.train.start, end = seis.train.end), side=2, filter=c(0.5, rep(1,min_h_seasonality-1), 0.5)/min_h_seasonality),
#`pgram <- spec.pgram(build_ts(seis.h, start = seis.train.start, end = seis.train.end),
                    detrend=F, demean=T, na.action=na.aggregate, plot=F)
pgram.data <- data.frame(freq=pgram$freq, spec=pgram$spec)
ggplot(pgram.data) +
  geom_line(aes(freq, spec)) +
  xlab("frequency") + ylab("spectrum") +
  labs(title = "Periodgram", caption = paste0("bandwidth = ", pgram$bandwidth, "    df = ", pgram$df)) ->
  periodgram

@@

ratio.color <- function(x) ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*3), "red", ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*2), "blue", ifelse(x >= (mean(pgram$spec) + sd(pgram$spec)*1), "darkgreen", "orange")))
shown_labels <- 4
periodgram +
  scale_x_continuous(sec.axis = sec_axis(~1/./3600, breaks=c(1, 3, 2*c(1,2,3,4,6,12), 24*7), labels = as.integer, name="hours")) +
  scale_y_continuous(sec.axis = sec_axis(~., breaks=mean(pgram$spec) + sd(pgram$spec) * c(1,3), labels=c("1", "2", "3")[c(1,3)], name="spectrum/sd ratio")) +
  geom_hline(yintercept=(mean(pgram$spec) + sd(pgram$spec) * c(1:3)), linetype="dotted", color = ratio.color(mean(pgram$spec) + sd(pgram$spec) * c(1:3))) +
  geom_point(data=data.frame(freq=top95freq, spec=top95pc), aes(freq, (spec), color=ratio.color(spec)), shape="o", size=4, show.legend = F) +
  geom_label_repel(data=data.frame(freq=top95freq, spec=top95pc)[1:shown_labels,], aes(freq, (spec), label=round(1/freq/3600), color=ratio.color(spec)), segment.color="grey", show.legend=F) +
  scale_color_manual(values = c("darkgreen", "blue", "red")[start_ratio:3])
